---
title: 'Replication #3'
author: "Jack Schroeder"
date: "3/5/2019"
output:
  pdf_document: default
---
## Abstract
```{r setup, include=FALSE, warning=FALSE, results = "asis"}
knitr::opts_chunk$set(echo = TRUE)

# Tables 1 and 3 and All Figures

# I begin by loading Acharya et al's libraries.
# Most of these are already installed, but some (like maps and cem)
# need to be installed before running the code. Cem requires XQuartz,
# which I did not have installed.

# Two files - both ending in ind.csv - could not be committed to GitHub due to size. They can be
# downloaded off the dataverse:
# https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/CAEEG7.

library(foreign)
library(plyr)
library(reshape)
library(sandwich)
library(maps)
library(stargazer)
library(AER)
library(Formula)
library(lme4)
library(cem)
library(latticeExtra)
library(stringr)

# This source code contains functions and colors (like tangy blue!).

source("Dataverse_Files/panel-utils.R")

# The fips file contains state FIPS (Federal Information Processing Standard) data.

data(state.fips)

# From there the authors do some work manipulating the data and saving it as fips.state.

state.fips <- unique(state.fips[,c("fips","abb")])
state.fips$abb <- as.character(state.fips$abb)

# It appears there was some trouble with Alaska and Hawaii, which the authors fix.

state.fips <- rbind(state.fips, c(2, "AK"))
state.fips <- rbind(state.fips, c(15, "HI"))
rownames(state.fips) <- state.fips$abb
fips.state <- state.fips
rownames(fips.state) <- fips.state$fips

# They also load in county FIPS data.

data(county.fips)

# Then they create three new colors. A real shame the study was in black and white.

dodgerblue.30 <- rgb(30, 144, 255, 76.5, max =255)
indianred.30 <- rgb(205, 92, 92, 76.5, max =255)
indianred.75 <- rgb(205, 92, 92, 191, max =255)

# They make a function to compute clustered-standard errors. It comes from Mahmood
# Arai and requires the libraries 'sandwich' and 'lmtest'. I would like to hear more
# about clustered standard errors in class if possible, since they are a bit confusing.
# From there, I am not really sure what the function is doing.

# Also the fact that the link they give to explain their method doesn't work isn't all 
# that helpful to me.

robust.se <- function(fm, clvar){
  library(sandwich);library(lmtest);
  x <- eval(fm$call$data, envir = parent.frame())
  if ("polr" %in% class(fm)) {
    require(MASS)
    cluster <- x[rownames(predict(fm, type = "probs")), clvar]
  } else {
    cluster <- x[names(predict(fm)), clvar]
  }
  M <- length(unique(cluster))
  N <- length(cluster)
  K <- dim(vcov(fm))[1]
  dfc <- (M/(M-1))*((N-1)/(N-K))
  uj  <- apply(estfun(fm),2, function(x) tapply(x, cluster, sum));
  vcovCL <- dfc*sandwich(fm, meat=crossprod(uj)/N)
  coeftest(fm, vcovCL)
}

# This function will help put checkmarks in the tables. It is fairly simple latek 
# formatting.

ch.row <- function(name, yesno) {
    c(name, ifelse(yesno, "$\\checkmark$", ""))
}

```

```{r csvs, cache=TRUE, echo=FALSE}

# They then read in three csv files (and make sure strings are not read in as factors).
# Preceptor would change these to read_csv. I just don't want to mess up the rest of 
# their study before making a semantic change.

# The first contains county data. Lots of it is location or race-based. Some interesting
# stats in here, like `pdem1856`.

countydata <- read.csv("Dataverse_Files/abs-jop-countydata.csv", stringsAsFactors = FALSE)

# wh.counties is the data from individual respondents from the ANES survey in white
# counties. Or is it data from white respondents? Unclear.

wh.counties <- read.csv("Dataverse_Files/abs-jop-cces-white-countydata.csv", stringsAsFactors = FALSE)

# Then they read in the total respondents from the CCES (Cooperative Congressional
# Election Study).

cces.comb <- read.csv("Dataverse_Files/abs-jop-cces-ind.csv", stringsAsFactors = FALSE)

# I also read in the nes.comb csv file up here so I can cache them all at once.

nes.comb <- read.csv("Dataverse_Files/abs-jop-nes-ind.csv", stringsAsFactors = FALSE)

# They read in NES data on white counties with read.csv.
# This should probably be ANES but that's beside the point.

nes.counties <- read.csv("Dataverse_Files/abs-jop-nes-white-countydata.csv", stringsAsFactors = FALSE)
```

```{r continuation, echo=FALSE}

# Then they read in the states they're looking at: states in the Confederacy plus MO
# and KY (who, contrary to popular belief, remained in the Union). They comb their
# datasets for these states. They multiply by 1 probably to return only 1 and 0 values
# (and not T/F).

st.list <- c("AL", "AR", "GA", "FL", "KY", "LA", "MS", "MO", "NC", "SC", "TN", "TX", "VA","WV")
cces.comb$abs.sample <- 1 * (cces.comb$state.abb %in% st.list)
wh.counties$abs.sample <- 1 * (wh.counties$state.abb %in% st.list)
countydata$abs.sample <- 1 * (countydata$state.abb %in% st.list)

# They also mess with the tractor growth column for reasons unknown.

wh.counties$tractor.growth <- (wh.counties$tractors40 - wh.counties$tractors30)

# They relevel the income category in cces.comb, along with creating some datasets
# based off race.

cces.comb$inc.cat <- factor(cces.comb$inc.cat, levels = c("<20k", "20-50k", "50-100k", "100-150k", "150k+"))
whites <- cces.comb[which(cces.comb$white == 1),]
blacks <- cces.comb[which(cces.comb$black == 1),]
latinos <- cces.comb[which(cces.comb$latino == 1),]
others <- cces.comb[which(cces.comb$white != 1 & cces.comb$black != 1 & cces.comb$latino != 1),]

# Then they grab Southerner-specific data.

southerners <- subset(cces.comb, abs.sample == 1)
s.whites <- subset(whites, abs.sample == 1)
s.blacks <- subset(blacks, abs.sample == 1)
s.latinos <- subset(latinos, abs.sample == 1)

# They make sure to add state and county FIPS data.

s.whites$state.abb <- factor(s.whites$state.abb)
s.blacks$state.abb <- factor(s.blacks$state.abb)
s.latinos$state.abb <- factor(s.latinos$state.abb)
south.counties <- subset(wh.counties, abs.sample == 1)
south.counties$state.abb <- factor(south.counties$state.abb)
south.counties <- south.counties[order(as.numeric(south.counties$fips)),]

# They do a similar abs.sample as above, multiplying by 1 to return binary values.

nes.counties$abs.sample <- 1 * (nes.counties$state.abb %in% st.list)

# They read in another csv to use for combing the NES data, again making an abs.sample
# column that's multiplied by 1.

nes.comb$abs.sample <- 1 * (nes.comb$state.abb %in% st.list)

# They create nes.whites and nes.blacks based on racial data in nes.comb.

nes.whites <- nes.comb[which(nes.comb$white == 1),]
nes.blacks <- nes.comb[which(nes.comb$black == 1),]

# This chunk subsets nes.whites based on race and sample. They add abbreviations.
ns.whites <- subset(nes.whites, abs.sample == 1)
ns.blacks <- subset(nes.blacks, abs.sample == 1)
ns.whites$state.abb <- factor(ns.whites$state.abb)
ns.blacks$state.abb <- factor(ns.blacks$state.abb)

# This is the formula they create for looking at 1860 Census Data.

base1860.form <- formula(. ~ pslave1860 + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2)+ rugged  + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860  + rail1860 + water1860 + state.abb)

# This looks at individual data.

ind.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ) +  inc.cat +religion + female + age + state.abb*as.factor(year))

# This looks at individual data including interaction variables.

ind.int.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ)*pslave1860 + inc.cat*pslave1860 + religion*pslave1860 + female*pslave1860 + age*pslave1860  + state.abb*as.factor(year))

# This data looks at contextual data (county? time? Unclear).

context.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ) + inc.cat  +religion +female + age + blkprop.z00 + log(medinc.z10) + w.unemp.rate2014 + log(wbincratio2014) + state.abb*as.factor(year))

# This looks at context but with interactions. 

context.int.form <- formula(. ~ pslave1860   + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2) + rugged + land.ineq1860 + sfarmprop1860 + log(totpop1860) + log(fvalpac1860) + log(acimp1860) + fbprop1860 + rail1860 + water1860 + as.factor(educ) +  inc.cat  +religion +female + age + blkprop.z00*pslave1860 + log(medinc.z10)*pslave1860 + w.unemp.rate2014*pslave1860 + log(wbincratio2014)*pslave1860 + state.abb*as.factor(year))

# For instrumental-variable regression (a topic I know little about), they use the Formula
# packages. I understand this to mean they take a quasi-experimental approach and infer 
# randomization at some point.

base.iv.form <- Formula(. ~ pslave1860 + log(coarea00) + rugged + latitude + I(latitude^2) + longitude + I(longitude^2)  + water1860  + state.abb | cottonsuit + log(coarea00) + rugged  + latitude + I(latitude^2) + longitude + I(longitude^2) + water1860  + state.abb)

# They return to making normal formulas (this one is a base formula, which is not the reduced
# form).

base.first.form <- formula(pslave1860 ~ cottonsuit + log(coarea00) + rugged + latitude + I(latitude^2) + longitude + I(longitude^2)  +water1860 + state.abb)

# This one looks at the reduced form check, which is currently just statistical jargon to me.

rform.form <- formula(. ~  cottonsuit + log(coarea00) + rugged + latitude + I(latitude^2)+ longitude + I(longitude^2)  + water1860+  state.abb)




```
## Figure 2
```{r fig2, echo=FALSE, results="asis", warning=FALSE}

# Creating Figure 2 involves a lot of code in base R. We essentially take data from southern
# counties and plot a few things - proportion democrat, affirmative action, 
# racial resentment, white/black thermometer score - against proportion slave in 1860.

par(mfrow = c(1,4), mar = 0.1 + c(4, 3, 2, 0.5), cex.main = 1)
plot(south.counties$pslave1860, south.counties$dem, pch = 19, col = "#33333333", xlab = "Proportion Slave, 1860", ylab = "", main = "Proportion Democrat", yaxt = "n", cex = south.counties$sample.size/100)
axis(side = 2, las = 2)
abline(lm(dem ~ pslave1860, data = south.counties, weights = sample.size), lwd = 2, col = "#AA0000")
plot(south.counties$pslave1860, south.counties$affirm, pch = 19, col = "#33333333", xlab = "Proportion Slave, 1860", ylab = "", main = "Affirmative Action", yaxt = "n", cex = south.counties$sample.size/100)
axis(side = 2, las = 2)
abline(lm(affirm ~ pslave1860, data = south.counties, weights = sample.size), lwd = 2, col = "#AA0000")
plot(south.counties$pslave1860, south.counties$resent, pch = 19, col = "#33333333", xlab = "Proportion Slave, 1860", ylab="", main = "Racial Resentment", yaxt = "n", cex = south.counties$sample.size.res/75)
axis(side = 2, las = 2)
abline(lm(resent ~ pslave1860, data = south.counties, weights = sample.size.res), lwd = 2, col = "#AA0000")
with(subset(nes.counties, state.abb %in% st.list), plot(pslave1860, wtherm-btherm, cex = sample.size.bt/40, pch = 19, col = "#33333333", xlab = "Proportion Slave, 1860", ylab = "", main = "White - Black Therm. Score", las = 1, xlim = c(0, 0.9)))
abline(lm(I(wtherm-btherm) ~ pslave1860, weights = sample.size.bt, data = subset(nes.counties, state.abb %in% st.list)), lwd = 2, col = "#AA0000")
```

## Table 1
Table 1 does not print with checkmarks.
```{r t1, echo=FALSE, results="asis", warning=FALSE}
library(stargazer)
# They create the models they analyze. The first looks at
# proportion democrat and is weighted at the county level.

cnty.res <- lm(dem ~ pslave1860, data = south.counties, weights = sample.size)

# This model is not included in Table 1.

cnty.res.fe <- lm(dem ~ pslave1860 + state.abb, data = south.counties, weights = sample.size)

# The second looks at proportion democrat but includes state
# fixed effects and 1860 covariates. It uses the base 1860
# formula.

cnty.res.full <- lm(update(base1860.form, dem ~ .), data = south.counties, weights = sample.size)

# These two models are not in Table 1.

cnty.aff <- lm(affirm ~ pslave1860, data = south.counties, weights = sample.size)
cnty.aff.fe <- lm(affirm ~ pslave1860 + state.abb, data = south.counties, weights = sample.size)

# This model is the third in Table 1 and analyzes support for
# affirmative action using the base 1860 formula.

cnty.aff.full <- lm(update(base1860.form, affirm ~ .), data = south.counties, weights = sample.size)

# These two models are not used in Table 1.
cnty.resent <- lm(resent ~ pslave1860, data = south.counties, weights = sample.size.res)
cnty.resent.fe <- lm(resent ~ pslave1860 +  state.abb, data = south.counties, weights = sample.size.res)

# This model is the fourth model in the table and analyzes
# racial resentment using the base 1860 formula. It has
# clustered standard errors.

cnty.resent.full <- lm(update(base1860.form, resent ~ .), data = south.counties, weights = sample.size.res)

# These models look at individual results, which are necessary
# for the fifth model in Table 1.

therm.mod <- lm(therm.diff ~ pslave1860, data = ns.whites, weights = weight)
therm.mod.rse <- robust.se(therm.mod, clvar = "fips")

therm.mod.fe <- lm(therm.diff ~ pslave1860 + state.abb*as.factor(year), data = ns.whites, weights = weight)
therm.mod.fe.rse <- robust.se(therm.mod.fe, clvar = "fips")

therm.1860 <- lm(update(base1860.form, therm.diff ~ . + state.abb*as.factor(year)), data = ns.whites, weights = weight)
therm.1860.rse <- robust.se(therm.1860, clvar = "fips")

# This stargazer code replicates Table 1, although not perfectly.
# The checkmarks are missing (even though they made a function
# to create them) and the table just looks nasty. Not a fan.

tab1.alt <- stargazer(cnty.res, cnty.res.full, cnty.aff.full, cnty.resent.full, therm.1860,
                      se = list(NULL, NULL, NULL, NULL, therm.1860.rse[,2]),
                  keep = "pslave1860", style = "apsr", omit.stat = c("adj.rsq","ll", "F", "ser"),
                  covariate.labels = c("Prop. Slave, 1860"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 4), c("Level", "County", "County", "County", "County", "Individual"), ch.row("1860 Covariates", c(FALSE, rep(TRUE,3), FALSE)), ch.row("State Fixed Effects", c(FALSE, rep(TRUE,4))), ch.row("State-Year Fixed Effects", c(rep(FALSE,4), TRUE)), ch.row("Clustered SEs", c(rep(FALSE,4), TRUE)), rep("", 4)), multicolumn = TRUE)

```
Note. Models 1–4 are weighted least squares at the county level, with within-county sample sizes, adjusted by sampling weights, as weights. Model 5 is
weighted least squares at the individual level with state-year fixed effects. Standard errors, in parentheses, are clustered at the county level in model 5. There
are 50 counties in model 5.
```{r, include=FALSE, warning=FALSE}
## Instrumental Variables
cnty.iv <- ivreg(update(base.iv.form, dem ~ .), data = south.counties, weights = sample.size)

cnty.aff.iv <- ivreg(update(base.iv.form, affirm  ~ .), data = south.counties, weights = sample.size)

cnty.resent.iv <- ivreg(update(base.iv.form, resent  ~ .), data = south.counties, weights = sample.size.res)

therm.cty.iv <- ivreg(update(base.iv.form, therm.diff ~ .), data = nes.counties, weights = sample.size.td, subset = abs.sample == 1)

cnty.res.first <- lm(base.first.form, data = south.counties)


iv.tab <- stargazer(cnty.res.first, cnty.iv, cnty.aff.iv, cnty.resent.iv,
          keep = c("cotton", "pslave1860"), style = "apsr", omit.stat = c("ll", "rsq", "adj.rsq", "ser"),
                    covariate.labels = c("Cotton Suitability", "Prop. Slave, 1860"), dep.var.labels = c("Prop Slave", "Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 5), ch.row("State Fixed Effects", rep(TRUE,4)), ch.row("Geographic Controls", rep(TRUE,4)), c("Model", rep("2SLS", 4)), c("", "First Stage", rep("Second Stage", 3)), rep("", 5)), multicolumn = TRUE, model.names = FALSE)
iv.tab[4] <- "\\\\[-1.8ex] & Prop. Slave & Prop. Democrat & Affirm. Action & Racial Resentment \\\\ "
iv.tab <- gsub("\\{\\*\\}", "\\{\\\\dagger\\}", iv.tab)
iv.tab <- gsub("\\{\\*\\*\\}", "\\{\\*\\}", iv.tab)
iv.tab <- gsub("\\{\\*\\*\\*\\}", "\\{\\*\\*\\}", iv.tab)
iv.tab <- iv.tab[-(length(iv.tab)-1)]
cat(paste(iv.tab, collapse = "\n"), "\n")

iv.tab.alt <- stargazer(cnty.res.first, cnty.iv, cnty.aff.iv, cnty.resent.iv, therm.cty.iv,
          keep = c("cotton", "pslave1860"), style = "apsr", omit.stat = c("ll", "rsq", "adj.rsq", "ser"),
                    covariate.labels = c("Cotton Suitability", "Prop. Slave, 1860"), dep.var.labels = c("Prop Slave", "Prop Democrat", "Affirm. Action", "Racial Resentment", "BW"), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 5), ch.row("State Fixed Effects", rep(TRUE,5)), ch.row("Geographic Controls", rep(TRUE,5)), c("Model", rep("2SLS", 5)), c("", "First Stage", rep("Second Stage", 4)), rep("", 5)), multicolumn = FALSE, model.names = FALSE)
iv.tab.alt[4] <- "\\\\[-1.8ex] & Proportion & Proportion & Support for & Racial  & White-Black  \\\\ "
iv.tab.alt <- append(iv.tab.alt, " & Slave, 1860 & Democrat & Affirm. Action &  Resentment & Therm. Diff  \\\\ ", after = 4)
iv.tab.alt <- gsub("\\{\\*\\}", "\\{\\\\dagger\\}", iv.tab.alt)
iv.tab.alt <- gsub("\\{\\*\\*\\}", "\\{\\*\\}", iv.tab.alt)
iv.tab.alt <- gsub("\\{\\*\\*\\*\\}", "\\{\\*\\*\\}", iv.tab.alt)
iv.tab.alt <- iv.tab.alt[-(length(iv.tab.alt)-1)]
cat(paste(iv.tab.alt, collapse = "\n"), "\n")
##cat(paste(iv.tab.alt, collapse = "\n"), "\n", file = "../tables/iv-table.tex")

### Reduced form check in the north


cnty.dem.rform <- lm(update(rform.form, dem ~ .), data = south.counties, weights = sample.size)

cnty.dem.ns.rform <- lm(update(rform.form, dem ~ .), data = wh.counties, weights = sample.size, subset = !(state.abb %in% st.list) & !(state.abb %in% c("MD", "DE","KY", "MO", "WV")))

cnty.aff.rform <- lm(update(rform.form, affirm ~ .), data = south.counties, weights = sample.size)

cnty.aff.ns.rform <- lm(update(rform.form, affirm ~ .), data = wh.counties, weights = sample.size, subset = !(state.abb %in% st.list) & !(state.abb %in% c("MD", "DE","KY", "MO", "WV")))

cnty.resent.rform <- lm(update(rform.form, resent ~ .), data = south.counties, weights = sample.size.res)

cnty.resent.ns.rform <- lm(update(rform.form, resent ~ .), data = wh.counties, weights = sample.size.res, subset = !(state.abb %in% st.list) & !(state.abb %in% c("MD", "DE","KY","MO", "WV")))

cnty.therm.rform <- lm(update(rform.form, therm.diff ~ .), data = nes.counties, weights = sample.size.td, subset = abs.sample == 1)

cnty.therm.ns.rform <- lm(update(rform.form, therm.diff ~ .), data = nes.counties, weights = sample.size.td, subset = abs.sample == 0 &  !(state.abb %in% c("MD", "DE","KY","MO", "WV")))

rform.tab <- stargazer(cnty.dem.rform, cnty.dem.ns.rform, cnty.aff.rform, cnty.aff.ns.rform, cnty.resent.rform, cnty.resent.ns.rform,
          keep = "cotton", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("FAO Cotton Suitability"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"),
          title = "Reduced form of the instrumental variables estimates for the South (columns 1, 3, and 5) and the North (columns 2, 4, and 6).", label = "t:falsification", column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE,6)), ch.row("Geographic Controls", rep(TRUE,6)), rep("", 7)), multicolumn = TRUE)
rform.tab[4] <- "\\\\[-1.8ex] &  \\multicolumn{2}{c}{Prop. Democrat} & \\multicolumn{2}{c}{Affirm. Action} & \\multicolumn{2}{c}{Racial Resentment} \\\\ "
rform.tab <- append(rform.tab, "\\\\[-1.8ex] & South & Non-South & South & Non-South & South & Non-South \\\\ ", after = 5)
rform.tab <- gsub("\\{\\*\\}", "\\{\\\\dagger\\}", rform.tab)
rform.tab <- gsub("\\{\\*\\*\\}", "\\{\\*\\}", rform.tab)
rform.tab <- gsub("\\{\\*\\*\\*\\}", "\\{\\*\\*\\}", rform.tab)
rform.tab <- rform.tab[-(length(rform.tab)-1)]
cat(paste(rform.tab, collapse = "\n"), "\n")
##cat(paste(rform.tab, collapse = "\n"), "\n", file = "../tables/reduced-form.tex")


## NES Results County
therm.cty.mod <- lm(therm.diff ~ pslave1860, data = nes.counties, weights = sample.size.td, subset = abs.sample == 1)

therm.cty.mod.fe <- lm(therm.diff ~ pslave1860 + state.abb, data = nes.counties, weights = sample.size.td, subset = abs.sample == 1)

therm.cty.1860 <- lm(update(base1860.form, therm.diff ~ .), data = nes.counties, weights = sample.size.td, subset = abs.sample == 1)

therm.cty.iv <- ivreg(update(base.iv.form, therm.diff ~ .), data = nes.counties, weights = sample.size.td, subset = abs.sample == 1)


therm.ind <- lm(update(base1860.form, I(wtherm-btherm) ~ .  + as.factor(year)*state.abb + female + age + I(age^2) + inc.mid + as.factor(educ) + religion), data = ns.whites, weights = weight)
therm.ind.rse <- robust.se(therm.ind, clvar = "fips")

## LA, NC, AR need to be dropped due to lack of state-year variation
## results the same with separate state and year fixed effects
therm.iv <- ivreg(update(base.iv.form, I(wtherm-btherm) ~ . + as.factor(year)*state.abb | . + as.factor(year)*state.abb), data = ns.whites, weights = weight, subset = !(state.abb %in% c("LA", "NC","AR", "WV")))
therm.iv.rse <- robust.se(therm.iv, clvar = "fips")

therm.iv.first <- lm(update(base.first.form, . ~ . + as.factor(year)*state.abb), data = ns.whites, weights = weight, subset = !(state.abb %in% c("LA", "NC","AR", "WV")))

btherm.1860 <- lm(update(base1860.form, btherm ~ . + as.factor(year)*state.abb), data = ns.whites, weights = weight)
btherm.1860.rse <- robust.se(btherm.1860, clvar = "fips")

## LA, NC, AR need to be dropped due to lack of state-year variation
## results the same with separate state and year fixed effects
btherm.iv <- ivreg(update(base.iv.form, btherm ~ . + as.factor(year)*state.abb | . + as.factor(year)*state.abb), data = ns.whites, weights = weight, subset = !(state.abb %in% c("LA", "NC","AR", "WV")))
btherm.iv.rse <- robust.se(btherm.iv, clvar = "fips")

wtherm.1860 <- lm(update(base1860.form, wtherm ~ . + as.factor(year)*state.abb), data = ns.whites, weights = weight)
wtherm.1860.rse <- robust.se(wtherm.1860, clvar = "fips")

## LA, NC, AR need to be dropped due to lack of state-year variation
## results the same with separate state and year fixed effects
wtherm.iv <- ivreg(update(base.iv.form, wtherm ~ . + as.factor(year)*state.abb | . + as.factor(year)*state.abb), data = ns.whites, weights = weight, subset = !(state.abb %in% c("LA", "NC","AR")))
wtherm.iv.rse <- robust.se(wtherm.iv, clvar = "fips")


therm.tab <- stargazer(therm.mod, therm.mod.fe, therm.1860, therm.iv,
          keep = "pslave1860", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860"), dep.var.labels = c("White Thermometer - Black Thermometer (-100 to 100)"), se = list(therm.mod.rse[,2], therm.mod.fe.rse[,2], therm.1860.rse[,2], therm.iv.rse[,2]), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 5), ch.row("Clustered SEs", rep(TRUE,4)), ch.row("State-Year Fixed Effects", c(FALSE, rep(TRUE,3))), ch.row("Geographic Controls", c(rep(FALSE, 2), rep(TRUE,2))), ch.row("1860 Covariates", c(FALSE, FALSE, TRUE, FALSE)), rep("", 7)), multicolumn = TRUE)
therm.tab[4] <- "\\\\[-1.8ex] &  \\multicolumn{4}{c}{White Thermometer - Black Thermometer (-100 to 100)} \\\\ "
therm.tab[5] <- "\\\\[-1.8ex] &  \\multicolumn{3}{c}{OLS} & IV \\\\ "
therm.tab <- therm.tab[-6]
therm.tab <- gsub("\\{\\*\\}", "\\{\\\\dagger\\}", therm.tab)
therm.tab <- gsub("\\{\\*\\*\\}", "\\{\\*\\}", therm.tab)
therm.tab <- gsub("\\{\\*\\*\\*\\}", "\\{\\*\\*\\}", therm.tab)
therm.tab <- therm.tab[-(length(therm.tab)-1)]
therm.tab <- append(therm.tab, paste("First-stage t-statistic & & & & ", round(summary(therm.iv.first)$coef[2,3], 2), "$^{**}$ \\\\", sep = ""), length(therm.tab)-2)
cat(paste(therm.tab, collapse = "\n"), "\n")
##cat(paste(therm.tab, collapse = "\n"), "\n", file = "../tables/therm-tab.tex")

septherm.tab <- stargazer(btherm.1860, btherm.iv, wtherm.1860, wtherm.iv,
          keep = "pslave1860", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860"), dep.var.labels = c("Black Therm. Scores", "White Therm. Scores"), se = list(btherm.1860.rse[,2], btherm.iv.rse[,2], wtherm.1860.rse[,2], wtherm.iv.rse[,2]), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 5), ch.row("Clustered SEs", rep(TRUE,4)), ch.row("State-Year Fixed Effects", rep(TRUE,4)), ch.row("Geographic Controls", rep(TRUE,4)), ch.row("1860 Covariates", c(TRUE, FALSE, TRUE, FALSE)), rep("", 7)), multicolumn = TRUE)
septherm.tab[4] <- "\\\\[-1.8ex] &  \\multicolumn{2}{c}{Black Therm. Scores} &  \\multicolumn{2}{c}{White Therm. Scores} \\\\ "
septherm.tab[5] <- "\\\\[-1.8ex] &  OLS & IV &  OLS & IV \\\\ "
septherm.tab <- septherm.tab[-6]
septherm.tab <- gsub("\\{\\*\\}", "\\{\\\\dagger\\}", septherm.tab)
septherm.tab <- gsub("\\{\\*\\*\\}", "\\{\\*\\}", septherm.tab)
septherm.tab <- gsub("\\{\\*\\*\\*\\}", "\\{\\*\\*\\}", septherm.tab)
septherm.tab <- septherm.tab[-(length(septherm.tab)-1)]
cat(paste(septherm.tab, collapse = "\n"), "\n")
##cat(paste(septherm.tab, collapse = "\n"), "\n", file = "../tables/therm-separate.tex")


ctytherm.tab <- stargazer(therm.cty.mod, therm.cty.mod.fe, therm.cty.1860, therm.cty.iv,
          keep = "pslave1860", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860"), dep.var.labels = c("White Thermometer - Black Thermometer (-100 to 100)"), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 5), ch.row("Clustered SEs", rep(TRUE,4)), ch.row("State-Year Fixed Effects", rep(TRUE,4)), ch.row("Geographic Controls", rep(TRUE,4)), ch.row("1860 Covariates", c(TRUE, FALSE, TRUE, FALSE)), rep("", 7)), multicolumn = TRUE)
ctytherm.tab[4] <- "\\\\[-1.8ex] &  \\multicolumn{4}{c}{White Thermometer - Black Thermometer (-100 to 100)} \\\\ "
ctytherm.tab[5] <- "\\\\[-1.8ex] &  \\multicolumn{3}{c}{OLS} & IV \\\\ "
ctytherm.tab <- ctytherm.tab[-6]
ctytherm.tab <- gsub("\\{\\*\\}", "\\{\\\\dagger\\}", ctytherm.tab)
ctytherm.tab <- gsub("\\{\\*\\*\\}", "\\{\\*\\}", ctytherm.tab)
ctytherm.tab <- gsub("\\{\\*\\*\\*\\}", "\\{\\*\\*\\}", ctytherm.tab)
ctytherm.tab <- ctytherm.tab[-(length(ctytherm.tab)-1)]
cat(paste(ctytherm.tab, collapse = "\n"), "\n")
##cat(paste(ctytherm.tab, collapse = "\n"), "\n", file = "../tables/therm-county.tex")

## Neighbor matching
cnty.res.neighbor <- lm(update(base1860.form, dem ~ .), data = south.counties, weights = sample.size, subset = nmatch.diff.20 == 1)

cnty.aff.neighbor <- lm(update(base1860.form, affirm ~ .), data = south.counties, weights = sample.size, subset = nmatch.diff.20 == 1)

cnty.resent.neighbor <- lm(update(base1860.form, resent ~ .), data = south.counties, weights = sample.size.res, subset = nmatch.diff.20 == 1)

## Matching (Non-slave south versus north)
## Note that there will be some slight deviation from the results in
## the paper due to the random nature of k2k matching in this context
mdata <- wh.counties[which(!(wh.counties$state.abb %in% st.list) | wh.counties$pslave < 0.05),]
mdata <- mdata[which(!(mdata$state.abb %in% c("MD", "DE"))), ]
mvars <- c("dem", "affirm", "resent","south", "fvalpc1860", "fbprop1860", "totpop1860", "longitude", "latitude", "coarea00")
mdata$south <- 1 * (mdata$state.abb %in% st.list)
mout <- cem("south", data = mdata[,mvars], drop = c("dem", "affirm", "resent"), k2k = TRUE)

unique(mdata$state.abb[mout$w > 0 & mdata$south == TRUE])
unique(mdata$state.abb[mout$w > 0 & mdata$south == FALSE])

match.dem <- lm(update(base1860.form, dem ~ south + . - pslave1860 - state.abb), data = mdata, weights = sample.size, subset = mout$w > 0)

match.aff <- lm(update(base1860.form, affirm ~ south + . - pslave1860 - state.abb), data = mdata, weights = sample.size, subset = mout$w > 0)

match.resent <- lm(update(base1860.form, resent ~ south + . - pslave1860 - state.abb), data = mdata, weights = sample.size.res, subset = mout$w > 0)
```

## Table 2

```{r t2, echo=FALSE, warning=FALSE, results="asis"}
# Table 2
match.tab <- stargazer(cnty.res.neighbor, match.dem, cnty.aff.neighbor, match.aff, cnty.resent.neighbor, match.resent,
          dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), keep = c("pslave1860","south"), covariate.labels = c("Prop. Slave, 1860","Slave State"),
           style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(c(TRUE,FALSE),3)), ch.row("1860 Covariates", rep(TRUE, 6)), ch.row("50\\% Threshold Match", rep(c(TRUE,FALSE), 3)), ch.row("North-South Match", rep(c(FALSE,TRUE), 3)), rep("", 7)), multicolumn = TRUE)

```
Note. Model 1 is the first-stage relationship. Models 2–5 are weighted two-stage least-squares models, with weights as given in table 1. Standard errors are in
parentheses.


## OTHER
```{r t3, echo=FALSE, warning=FALSE, results = "asis"}
cor(south.counties$pslave1860, south.counties$blkprop00, use = "pairwise")

cnty.res.blk70.ptbias <- lm(update(base1860.form, dem ~ . + blkprop70), data =south.counties, weights = sample.size)

cnty.res.blk00.ptbias <- lm(update(base1860.form, dem ~ . + blkprop00), data =south.counties, weights = sample.size)

cnty.aff.blk70.ptbias <- lm(update(base1860.form, affirm ~ . + blkprop70), data = south.counties, weights = sample.size)

cnty.aff.blk00.ptbias <- lm(update(base1860.form, affirm ~ . + blkprop00), data = south.counties, weights = sample.size)


cnty.resent.blk70.ptbias <- lm(update(base1860.form, resent ~ . + blkprop70), data = south.counties, weights = sample.size.res)

cnty.resent.blk00.ptbias <- lm(update(base1860.form, resent ~ . + blkprop00), data = south.counties, weights = sample.size.res)


cnty.dem.blk00.first <- lm(update(base1860.form, dem ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =south.counties, weights = sample.size)

cnty.dem.blk00.iv <- ivreg(update(base.iv.form, I(dem - coef(cnty.dem.blk00.first)["blkprop00"]*blkprop00) ~ .), data = south.counties, weights = sample.size)

cnty.dem.blk00 <- lm(update(base1860.form, I(dem - coef(cnty.dem.blk00.first)["blkprop00"]*(blkprop00)) ~ .), data =south.counties, weights = sample.size)

cnty.aff.blk00.first <- lm(update(base1860.form, affirm ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =south.counties, weights = sample.size)

cnty.aff.blk00.iv <- ivreg(update(base.iv.form, I(affirm - coef(cnty.aff.blk00.first)["blkprop00"]*blkprop00) ~ .), data = south.counties, weights = sample.size)

cnty.aff.blk00 <- lm(update(base1860.form, I(affirm - coef(cnty.aff.blk00.first)["blkprop00"]*(blkprop00)) ~ .), data =south.counties, weights = sample.size)


cnty.resent.blk00.first <- lm(update(base1860.form, resent ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =south.counties, weights = sample.size.res)

cnty.resent.blk00.iv <- ivreg(update(base.iv.form, I(resent - coef(cnty.resent.blk00.first)["blkprop00"]*blkprop00) ~ .), data = south.counties, weights = sample.size.res)

cnty.resent.blk00 <- lm(update(base1860.form, I(resent - coef(cnty.resent.blk00.first)["blkprop00"]*(blkprop00)) ~ .), data =south.counties, weights = sample.size.res)



## bootstrap the SEs
set.seed(6251983)
boots <- 1000
cnty.dem.blk00.boots <- rep(NA, times = boots)
cnty.aff.blk00.boots <- rep(NA, times = boots)
cnty.resent.blk00.boots <- rep(NA, times = boots)
for (b in 1:boots) {
  sc.star <- south.counties[sample(1:nrow(south.counties), replace = TRUE),]
  boot.dem.first <- lm(update(base1860.form, dem ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =sc.star, weights = sample.size)
  boot.dem  <- lm(update(base1860.form, I(dem - coef(boot.dem.first)["blkprop00"]*(blkprop00)) ~ .), data =sc.star, weights = sample.size)
  cnty.dem.blk00.boots[b] <- coef(boot.dem)["pslave1860"]

  boot.aff.first <- lm(update(base1860.form, affirm ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =sc.star, weights = sample.size)
  boot.aff  <- lm(update(base1860.form, I(affirm - coef(boot.aff.first)["blkprop00"]*(blkprop00)) ~ .), data =sc.star, weights = sample.size)
  cnty.aff.blk00.boots[b] <- coef(boot.aff)["pslave1860"]

  boot.resent.first <- lm(update(base1860.form, resent ~ . + blkprop00 +log(totpop00) +highsch90 + unemp + log(medinc00) + wbincratio00), data =sc.star, weights = sample.size.res)
  boot.resent <- lm(update(base1860.form, I(resent - coef(boot.resent.first)["blkprop00"]*(blkprop00)) ~ .), data =sc.star, weights = sample.size.res)
  cnty.resent.blk00.boots[b] <- coef(boot.resent)["pslave1860"]

}

# Put bootstrapped SEs into a holder (we don't calculate the BSE for
# the other coefficients since we don't care about them and don't
# report them in the paper)
dem.bse <- summary(cnty.dem.blk00)$coef[,2]
dem.bse["pslave1860"] <- sd(cnty.dem.blk00.boots)
aff.bse <- summary(cnty.aff.blk00)$coef[,2]
aff.bse["pslave1860"] <- sd(cnty.aff.blk00.boots)
resent.bse <- summary(cnty.resent.blk00)$coef[,2]
resent.bse["pslave1860"] <- sd(cnty.resent.blk00.boots)
#save(list=c("cnty.dem.blk00.boots", "cnty.aff.blk00.boots", "cnty.resent.blk00.boots"), file = "blkprop00-seqg-boots.RData")

blkprop.tab <- stargazer(cnty.res.blk00.ptbias, cnty.dem.blk00, cnty.aff.blk00.ptbias, cnty.aff.blk00, cnty.resent.blk00.ptbias, cnty.resent.blk00,
          keep = c("pslave1860", "blkprop00"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"), se = list(NULL, dem.bse, NULL, aff.bse, NULL, resent.bse),
          covariate.labels = c("Prop. Slave, Direct Effect", "Prop. Black, 2000"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE, 6)), ch.row("1860 Covariates", rep(TRUE, 6)), ch.row("Bootstrapped SEs", rep(c(FALSE,TRUE), 3)), c("Model", rep(c("WLS", "Seq. g-est."), 3)), rep("", 7)), multicolumn = TRUE)

## Appendix Table
seqg.tab <- stargazer(cnty.dem.blk00.first, cnty.aff.blk00.first, cnty.resent.blk00.first,
          keep = c("pslave1860", "blkprop00", "totpop00", "highsch90", "unemp","medinc","wbincratio"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860","Prop. Black 2000", "Log Population, 2000", "Percent High School Graduates, 1990", "Unemployment, 1999", "Median Income, 2000", "White-Black Income Ratio, 2000"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 4), ch.row("State Fixed Effects", rep(TRUE, 3)), ch.row("1860 Covariates", rep(TRUE, 3)), rep("", 4)), multicolumn = FALSE)

## antebellum results

cnty.dem.houses <- lm(update(base1860.form, dem ~ . + slavesperhouse), data = south.counties, weights = sample.size)

cnty.aff.houses <- lm(update(base1860.form, affirm ~ . + slavesperhouse), data = south.counties, weights = sample.size)

cnty.resent.houses <- lm(update(base1860.form, resent ~ . + slavesperhouse), data = south.counties, weights = sample.size.res)

cnty.dem.mortrate <- lm(update(base1860.form, dem ~ . + I(log(s.mortrate/w.mortrate))), data = south.counties, weights = sample.size, subset = s.mortrate > 0)

cnty.aff.mortrate <- lm(update(base1860.form, affirm ~ . + I(log(s.mortrate/w.mortrate))), data = south.counties, weights = sample.size, subset = s.mortrate > 0)

cnty.resent.mortrate <- lm(update(base1860.form, resent ~ . + I(log(s.mortrate/w.mortrate))), data = south.counties, weights = sample.size.res, subset = s.mortrate > 0)


ante.tab <- stargazer(cnty.dem.mortrate, cnty.dem.houses, cnty.aff.mortrate, cnty.aff.houses, cnty.resent.mortrate, cnty.resent.houses,
          keep = c("pslave1860", "mortrate", "slavesperhouse"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860", "Log Relative Slave Mortality, 1860", "Avg. Residents per Slave Dwelling"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE, 6)), ch.row("1860 Covariates", rep(TRUE, 6)), rep("", 7)), multicolumn = FALSE)


## 1851 Gubernatorial elections in MS and GA
## see txt files accompanying these csv files for codebooks
## Data comes from ICPSR 00001

ga.votes <- read.csv("Dataverse_Files/ga-votes-1824-1860.csv", stringsAsFactors = FALSE)
ga.votes$cfips <- strtrim(ga.votes$V3, nchar(ga.votes$V3)-1)
ga.votes$fips <- as.numeric(paste(13, str_pad(ga.votes$cfips, 3, side = "left", pad = "0"), sep = ""))
is.na(ga.votes) <- ga.votes == 9999999
ga.votes$howell1851 <- ga.votes$V345/ga.votes$V348


ga.votes <- merge(ga.votes, countydata, by = "fips", all.x = TRUE, all.y = FALSE)


lattice::xyplot(howell1851 ~ sprop1850, data = ga.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, col.line = "indianred", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Howell Cobb Vote-share, 1851", panel =
                    function(x,y,...) {  panel.xyplot(x, y, ...)
                                         panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})

ms.votes <- read.csv("Dataverse_Files/ms-votes-1824-1860.csv", stringsAsFactors = FALSE)
ms.votes$cfips <- strtrim(ms.votes$V3, nchar(ms.votes$V3)-1)
ms.votes$fips <- as.numeric(paste(28, str_pad(ms.votes$cfips, 3, side = "left", pad = "0"), sep = ""))
is.na(ms.votes) <- ms.votes == 9999999
ms.votes$foote1851 <- ms.votes$V187/ms.votes$V190

ms.votes <- merge(ms.votes, countydata, by = "fips", all.x = TRUE, all.y = FALSE)


lattice::xyplot(foote1851 ~ sprop1850, data = ms.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, col.line = "indianred", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Henry Foote Vote-share, 1851", panel =
                    function(x,y,...) {  panel.xyplot(x, y, ...)
                                         panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})

#cairo_pdf(filename = "figs/ms-ga-1851-vote.pdf", family = "Minion Pro", height = 4.5, width = 9, pointsize = 11)
p1 <- lattice::xyplot(howell1851 ~ sprop1850, data = ga.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, ylim = c(0,1), col.line = "indianred", main = "Georgia Gubernatorial Election, 1851", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Howell Cobb Vote-share, 1851", panel =
                    function(x,y,...) {  panel.xyplot(x, y, ...)
                                         panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})
p2 <- lattice::xyplot(foote1851 ~ sprop1850, data = ms.votes, subset = state.abb %in% st.list , pch = 16, lwd = 4, ylim = c(0,1), col.line = "indianred", main = "Mississippi Gubernatorial Election, 1851", col = dodgerblue.30, xlab = "Proportion Slave, 1850", ylab = "Henry Foote Vote-share, 1851", panel =
                    function(x,y,...) {  panel.xyplot(x, y, ...)
                                         panel.smoother(x,y,method = "loess", col = "indianred", lwd = 4)})
plot(p1, position = c(0.0, 0, 0.49, 1), more = TRUE)
plot(p2, position = c(0.5, 0, 1, 1))
#dev.off()

den.cut <- quantile(south.counties$totpop1860/south.counties$coarea, na.rm = TRUE, probs = .9)

cnty.res.rural <- lm(update(base1860.form, dem ~ . ), data=south.counties, weights = sample.size, subset = totpop1860/coarea < den.cut)

cnty.aff.rural <- lm(update(base1860.form, affirm ~ .), data =south.counties, weights = sample.size, subset = totpop1860/coarea < den.cut)

cnty.resent.rural <- lm(update(base1860.form, resent ~ .), data =south.counties, weights = sample.size.res, subset = totpop1860/coarea < den.cut)

civil.fe <- lm(I(farmval - farmval1870)/farmval ~ pslave1860  + state.abb, data = countydata, subset = abs.sample == 1)

south.counties$civil.des <- with(south.counties, (farmval - farmval1870)/farmval)

cnty.dem.civil <- lm(update(base1860.form, dem ~ . + civil.des), data = south.counties, weights = sample.size)

cnty.aff.civil <- lm(update(base1860.form, affirm ~ . + civil.des), data = south.counties, weights = sample.size)

cnty.resent.civil <- lm(update(base1860.form, resent ~ . + civil.des), data = south.counties, weights = sample.size.res)

ruralciv.tab <- stargazer(cnty.res.rural, cnty.dem.civil, cnty.aff.rural, cnty.aff.civil, cnty.resent.rural, cnty.resent.civil,
          keep = c("pslave1860", "civil.des"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860", "Civil War Destruction"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(c(TRUE),6)), ch.row("1860 Covariates", rep(TRUE, 6)), ch.row("Dense 1860 Counties Dropped", rep(c(TRUE,FALSE), 3)), rep("", 7)), multicolumn = FALSE)



young.dem.1860 <- glm(update(base1860.form, dem ~ . + as.factor(year)*state.abb), data = s.whites, family=binomial(), weights = weights, subset = year - age > 1965)
young.dem.1860.rse <- robust.se(young.dem.1860, clvar = "fips")


young.aff.1860 <- glm(update(base1860.form, affirm ~ . + as.factor(year)*state.abb), data = s.whites, family=binomial(), weights = weights, subset = year - age > 1965)
young.aff.1860.rse <- robust.se(young.aff.1860, clvar = "fips")

young.resent.1860 <- lm(update(base1860.form, resent ~ . + as.factor(year)*state.abb), data = s.whites, weights = weights, subset = year - age > 1965)
young.resent.1860.rse <- robust.se(young.resent.1860, clvar = "fips")

young.tab <- stargazer(young.dem.1860, young.aff.1860, young.resent.1860,
          keep = "pslave1860", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser", "bic", "aic"),
          se = list(young.dem.1860.rse[,2],young.aff.1860.rse[,2], young.resent.1860.rse[,2]),
          covariate.labels = c("Prop. Slave, 1860", "1st/2nd Generation Immigrant", "Prop. Slave $\\times$ 1st/2nd Gen. Imm."), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 4), ch.row("State-Year Fixed Effects", rep(c(TRUE),3)), ch.row("1860 Covariates", rep(TRUE, 3)), rep("", 4)), multicolumn = FALSE)

## Lynchings - no data for TX, VA, WV
#countydata$popavg <- with(countydata, (totpop1880+totpop10+totpop20+totpop30+totpop40+totpop50)/6)
lynch.1860 <- lm(update(base1860.form, I(100000*lynchings/totpop20) ~ .), data = countydata, weights = coarea, subset = state.abb %in% st.list & !(state.abb %in% c("TX","VA","WV")))

lynch.iv <- ivreg(update(base.iv.form, I(100000*lynchings/totpop20) ~ .), data = countydata, weights = coarea, subset = state.abb %in% st.list & !(state.abb %in% c("DE","MD","TX", "VA", "WV")))


cnty.dem.tract <- lm(update(base1860.form, dem ~ pslave1860*tractor.growth + .), data = south.counties, weights = sample.size)

cnty.aff.tract <- lm(update(base1860.form, affirm ~ pslave1860*tractor.growth + .), data = south.counties, weights = sample.size)

cnty.resent.tract <- lm(update(base1860.form, resent ~ pslave1860*tractor.growth + .), data = south.counties, weights = sample.size.res)

quantile(south.counties$tractor.growth, probs = c(0.1, 0.9),na.rm = TRUE)
## CIs for 1st, 3rd quartiles using the sequential g-estimation approach
cnty.dem.tract.lo <- lm(update(base1860.form, I(dem - coef(cnty.dem.tract)['tractor.growth']*(tractor.growth - 0) - coef(cnty.dem.tract)['pslave1860:tractor.growth']*(tractor.growth-0)*pslave1860) ~ .), data = south.counties, weights = sample.size)

cnty.dem.tract.hi <- lm(update(base1860.form, I(dem - coef(cnty.dem.tract)['tractor.growth']*(tractor.growth - 0.07) - coef(cnty.dem.tract)['pslave1860:tractor.growth']*(tractor.growth-0.07)*pslave1860) ~ .), data = south.counties, weights = sample.size)

tractlynch.tab <- stargazer(lynch.1860, cnty.dem.tract, cnty.aff.tract, cnty.resent.tract,
          keep = c("pslave1860", "tractor.growth"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860", "Tractors Change, 1930-1940", "Prop Slave $\\times$ Tractors Change"), dep.var.labels = c("Lynchings", "Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 5), ch.row("State-Year Fixed Effects", rep(c(TRUE),4)), ch.row("1860 Covariates", rep(TRUE, 4)), rep("", 5)), multicolumn = FALSE)

tractors.lynch <- lm(update(base1860.form, I(lynchrate*100000) ~ tractor.growth + .), data = south.counties, subset = abs.sample == 1, weight = coarea)

tractors.ineq <- lm(update(base1860.form, I(blklwage1940-whtlwage1940) ~ tractor.growth + .), data = south.counties, subset = abs.sample == 1)

tractors.iv <- ivreg(update(base.iv.form, tractor.growth ~  .), data = south.counties, weights = coacres25)

tractcheck.tab <- stargazer(tractors.lynch, tractors.ineq,
          keep = c("tractor.growth", "pslave"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
                            dep.var.labels = c("Lynchings per 100,000 residents", "log(Black-White Wage Ratio)"), covariate.labels = c("Tractor Growth, 1930-1940", "Prop. Slave, 1860"), column.sep.width = "0pt", float = FALSE, header = FALSE, add.lines = list(rep("", 4), ch.row("State-Year Fixed Effects", rep(c(TRUE),3)), ch.row("1860 Covariates", rep(TRUE, 3)), rep("", 4)), multicolumn = FALSE)

btenancy.1860 <- lm(update(base1860.form, I(btenantprop25/100-wtenantprop25/100) ~ .), data = countydata, subset = state.abb %in% st.list, weights = coacres25)

btenancy.iv <- ivreg(update(base.iv.form, I(btenantprop25/100-wtenantprop25/100) ~  .), data = countydata, subset = state.abb %in% st.list & cottonsuit > 0, weights = coacres25)

bowner.1860 <- lm(update(base1860.form, I(bfarmerownerprop25-wfarmerownerprop25) ~ .), data = countydata, subset = state.abb %in% st.list, weights = coacres25)

bowner.iv <- ivreg(update(base.iv.form, I(bfarmerownerprop25-wfarmerownerprop25) ~  .), data = countydata, subset = state.abb %in% st.list, weights = coacres25)

intermed.tab <- stargazer(btenancy.1860, btenancy.iv, bowner.1860, bowner.iv,
          keep = "pslave1860", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860"), dep.var.labels = c("Black Tenant Share", "Share of Black Farmer Pop. Owning"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE, 4)), ch.row("Geographic Controls", rep(TRUE, 6)), ch.row("1860 Covariates", rep(c(TRUE,FALSE), 2)),rep("", 5)), multicolumn = TRUE, model.names = FALSE)

## Most county boundaries are set by 1925 or so.
## variables without the 1860 suffix are based on the 1860 county
## boundaries
pres.form <- formula(. ~ sprop + log(coarea00) + latitude + I(latitude^2) + longitude + I(longitude^2)+ rugged  + land.ineq + sfarmprop + log(totpop) + log(fvalpc) + log(acimp) + fbprop  + rail + water + state.abb)
pres.iv.form <- Formula(. ~ sprop + log(coarea00) + rugged + latitude + I(latitude^2) + longitude + I(longitude^2)  + water  + state.abb | cottonsuit + log(coarea00) + rugged  + latitude + I(latitude^2) + longitude + I(longitude^2) + water  + state.abb)
year.list <- seq(1840, 1964, by = 4)
outvars <- paste("pdem", year.list, sep = "")
pdemcoefs <- matrix(NA, nrow = length(outvars), ncol = 3)
pdemcoefs.nox <- matrix(NA, nrow = length(outvars), ncol = 3)
pdemcoefs.iv <- matrix(NA, nrow = length(outvars), ncol = 3)
pdemcoefs.rfns <- matrix(NA, nrow = length(outvars), ncol = 3)
pdemcoefs.rf <- matrix(NA, nrow = length(outvars), ncol = 3)
for (y in 1:length(outvars)) {
  if (!(outvars[y] %in% c("pdem1864", "pdem1868"))) {
    ## OLS
    ff <- as.formula(paste(outvars[y], " ~ ."))
    if (year.list[y] < 1924) {
      thismod <- lm(update(pres.form, ff), data = countydata, subset = state.abb %in% st.list)
    } else {
      thismod <- lm(update(base1860.form, ff), data = countydata, subset = state.abb %in% st.list)
    }
    pdemcoefs[y,1] <- 0.25*coef(thismod)[2]
    pdemcoefs[y,2:3] <- 0.25*confint(thismod)[2,]
    ## Only state FEs
    if (year.list[y] < 1924) {
      ff <- as.formula(paste(outvars[y], " ~ sprop + state.abb"))
    } else {
      ff <- as.formula(paste(outvars[y], " ~ pslave1860 + state.abb"))
    }
    thismod <- lm(ff, data = countydata, subset = state.abb %in% st.list)
    pdemcoefs.nox[y,1] <- 0.25*coef(thismod)[2]
    pdemcoefs.nox[y,2:3] <- 0.25*confint(thismod)[2,]
    ## IV
    if (year.list[y] < 1924) {
      ff <- update(pres.iv.form, as.formula(paste(outvars[y], "~ . | .")))
    } else {
      ff <- update(base.iv.form, as.formula(paste(outvars[y], "~ . | .")))
    }
    thismod <- ivreg(ff, data = countydata, subset = state.abb %in% st.list)
    pdemcoefs.iv[y,1] <- coef(thismod)[2]
    pdemcoefs.iv[y,2:3] <- confint(thismod)[2,]
    ## Reduced form in the non-south
    ff <- as.formula(paste(outvars[y], "~ cottonsuit + log(coarea00) + rugged+ latitude + I(latitude^2) + longitude + I(longitude^2)   + state.abb"))
    thismod <- lm(ff, data = countydata, subset = !(state.abb %in% st.list) & !(state.abb %in% c("MD", "DE", "MO")))
    pdemcoefs.rfns[y,1] <- coef(thismod)[2]
    pdemcoefs.rfns[y,2:3] <- confint(thismod)[2,]
    ## Reduced form in the south
    thismod <- lm(ff, data = countydata, subset = state.abb %in% st.list)
    pdemcoefs.rf[y,1] <- coef(thismod)[2]
    pdemcoefs.rf[y,2:3] <- confint(thismod)[2,]
  }
  ## if (outvars[y] %in% c("pdem1860","pdem1864")) {
  ##   pdemcoefs[y,1] <- NA
  ##   pdemcoefs[y,2:3] <- NA
  ##   pdemcoefs.iv[y,1] <- NA
  ##   pdemcoefs.iv[y,2:3] <- NA
  ## }
  ## if (outvars[y] == "pdem1856") {
  ##   pdemcoefs[y,1] <- NA
  ##   pdemcoefs[y,2:3] <- NA
  ## }
}

douglas.ols <- lm(update(pres.form, pdem1860 ~ .), data = countydata, subset = state.abb %in% st.list)
douglas.iv <- ivreg(update(pres.iv.form, pdem1860 ~ .), data = countydata, subset = state.abb %in% st.list)

wallace.ols <- lm(update(base1860.form, wallace68.alt ~ .), data = countydata, subset = state.abb %in% st.list)
wallace.iv <- ivreg(update(base.iv.form, wallace68.alt ~ .), data = countydata, subset = state.abb %in% st.list)
thurmond.ols <- lm(update(base1860.form, thurmond48 ~ .), data = countydata, subset = state.abb %in% st.list)
thurmond.iv <- ivreg(update(base.iv.form, thurmond48 ~ .), data = countydata, subset = state.abb %in% st.list)
obama.ols <- lm(update(base1860.form,  wht.obama.vote ~ .), data = countydata, subset = abs.sample == 1)
obama.iv <- ivreg(update(base.iv.form, wht.obama.vote  ~ .), data = countydata, subset = abs.sample == 1)

##cairo_pdf(file= "../figs/prescountyvote-iv.pdf", family = "Minion Pro", height = 4.5, width = 6.5, pointsize = 9)
plot(x = year.list, y = 0.25*pdemcoefs.iv[,1], ylim = range(c(.25*pdemcoefs.iv,25*confint(obama.iv)["pslave1860",]), na.rm = TRUE), xlim=c(min(year.list),2016), xlab = "Year",
     ylab = "Effect of Slavery on % Democrat", pch = 19, main = "Presidential Elections", bty = "n", yaxt = "n")
abline(v = 1904, lty = 2, col = "grey70")
text(x = 1904, y = 25*confint(obama.iv)["pslave1860",1]+0.5, "All states but KY have\nenacted poll taxes", pos = 4)
abline(v = 1965, lty = 2, col = "grey70")
text(x = 1965, y =  25*confint(obama.iv)["pslave1860",1]+0.5, "Voting Rights Act", pos = 4)
axis(side = 2, las = 2, cex = 0.8)
abline(h=0, col = "grey")
segments(x0 = year.list, y0 = .25*pdemcoefs.iv[,2], y1 = .25*pdemcoefs.iv[,3])
rect(xleft = 1860, xright = 1877, ybottom = -100, ytop=100, col = rgb(.5,.5,.5, alpha = 0.5), border = NA)
text(x = 1860, y = max(.25*pdemcoefs.iv, na.rm=TRUE)-1, "Civil War\nBegins", pos = 2)
text(x = 1877, y = max(.25*pdemcoefs.iv, na.rm=TRUE)-1, "Reconstruction\nEnds", pos = 4)
points(x = 1968, y = .25*coef(wallace.iv)["pslave1860"], pch = 17, col = "indianred")
segments(x0 = 1968, y0 = 0.25*confint(wallace.iv)["pslave1860",1], y1 = 0.25*confint(wallace.iv)["pslave1860",2], col = "indianred")
text(x = 1968, y = 0.25*coef(wallace.iv)["pslave1860"], "Wallace\n1968", pos = 4, col = "indianred")
points(x = 1949, y = .25*coef(thurmond.iv)["pslave1860"], pch = 17, col = "indianred")
segments(x0 = 1949, y0 = 0.25*confint(thurmond.iv)["pslave1860",1], y1 = 0.25*confint(thurmond.iv)["pslave1860",2], col = "indianred")
text(x = 1949, y = 0.35*confint(thurmond.iv)["pslave1860",2], "Thurmond\n1948", pos = 3, col = "indianred")
segments(x0=1949, y0=0.35*confint(thurmond.iv)["pslave1860",2],y1=0.26*confint(thurmond.iv)["pslave1860",2], lty = 3, col = "grey70")
points(x = 2008, y = 25*coef(obama.iv)["pslave1860"], pch = 19)
segments(x0 = 2008, y0 = 25*confint(obama.iv)["pslave1860",1], y1 = 25*confint(obama.iv)["pslave1860",2])
text(x = 2008, y = 25*coef(obama.iv)["pslave1860"], "Obama\n2008", pos = 4)
##dev.off()


##cairo_pdf(file= "../figs/prescountyvote-rform.pdf", family = "Minion Pro", height = 4, width = 6, pointsize = 9)
plot(x = year.list[year.list > 1868], y = pdemcoefs.rfns[year.list > 1868,1], ylim = range(c(pdemcoefs.rfns[year.list > 1868,], pdemcoefs.rf[year.list > 1868,]), na.rm = TRUE), xlab = "Year",
     ylab = "Effect of Cotton Suitability on % Democrat", pch = 19, main = "Presidential Elections", bty = "n", yaxt = "n")
points(x = year.list[year.list > 1868] + 1, y = pdemcoefs.rf[year.list > 1868,1], pch = 19, col = "indianred")
axis(side = 2, las = 2, cex = 0.8)
abline(h=0, col = "grey")
segments(x0 = year.list[year.list > 1868], y0 = pdemcoefs.rfns[year.list > 1868,2], y1 = pdemcoefs.rfns[year.list > 1868,3])
segments(x0 = year.list[year.list > 1868] + 1, y0 = pdemcoefs.rf[year.list > 1868,2], y1 = pdemcoefs.rf[year.list > 1868,3], col = "indianred")
##dev.off()


### Appendix tables

south.counties$lynchrate.scaled <- 100000*south.counties$lynchrate

sum.tab <- stargazer(south.counties[,c("dem", "affirm", "resent","lynchrate.scaled","coarea00", "rugged", "latitude", "longitude", "pslave1860", "land.ineq1860", "sfarmprop1860", "totpop1860", "fvalpac1860", "fbprop1860", "rail1860", "water1860", "cottonsuit", "blkprop00","tractor.growth")], covariate.labels = c("Prop. Democrat", "Support for Affirmative Action", "Racial Resentment", "Lynchings per 100,000 1920 Residents, 1882-1930", "County Area, 2000", "Ruggedness", "Latitude, 2000", "Longitude, 2000", "Prop. Slave, 1860", "Gini Coefficient for Land Holdings, 1860", "Prop. Small Farms ($<$ 50 Acres), 1860", "Total Population, 1860", "Farm Value per Capita, 1860", "Prop. Free Black, 1860", "Rail Access, 1860", "Water Acces, 1860", "Cotton Suitability", "Prop. Black, 2000", "Tractor Growth, 1930-1940"), float = FALSE, header = FALSE)

cces.sum.tab <- stargazer(s.whites[,c("dem", "affirm", "resent", "age", "religion", "female", "inc.mid")], covariate.labels = c("Democratic Identification", "Support for Affirmative Action", "Racial Resentment", "Age", "Religious Importance", "Gender (Female = 1, Male = 0)", "Household Income (Bracket Midpoint)"), header = FALSE, float = FALSE)
ns.whites$wb.thermdiff <- ns.whites$wtherm-ns.whites$btherm
anes.sum.tab <- stargazer(ns.whites[,c("btherm", "wtherm", "wb.thermdiff")], covariate.labels = c("Black Therm. Score", "White Therm. Score", "White-Black Therm. Difference"), header = FALSE, float = FALSE)

south.counties$slavesperwhite <- with(south.counties, stot1860/whtot1860)
## with alternative definition of slavery -- slaves per white
sph.dem <- lm(dem ~ log(1+slavesperwhite), data = south.counties, weights = sample.size)

sph.dem.fe <- lm(dem ~ log(1+slavesperwhite) + state.abb, data = south.counties, weights = sample.size)

sph.dem.full <- lm(update(base1860.form, dem ~ log(1+slavesperwhite) + . - pslave1860), data = south.counties, weights = sample.size)

sph.iv <- ivreg(update(base.iv.form, dem ~ log(1+slavesperwhite) + . - pslave1860), data = south.counties, weights = sample.size)

sph.aff <- lm(affirm ~ log(1+slavesperwhite), data = south.counties, weights = sample.size)

sph.aff.fe <- lm(affirm ~ log(1+slavesperwhite) + state.abb, data = south.counties, weights = sample.size)
summary(sph.aff.fe)

sph.aff.full <- lm(update(base1860.form, affirm ~ log(1+slavesperwhite) + . - pslave1860), data = south.counties, weights = sample.size)

sph.aff.iv <- ivreg(update(base.iv.form, affirm ~ log(1+slavesperwhite) + . - pslave1860), data = south.counties, weights = sample.size, subset = cottonsuit > 0)

sph.resent <- lm(resent ~ log(1+slavesperwhite), data = south.counties, weights = sample.size.res)

sph.resent.fe <- lm(resent ~ log(1+slavesperwhite) +  state.abb, data = south.counties, weights = sample.size.res)

sph.resent.full <- lm(update(base1860.form, resent ~ log(1+slavesperwhite) + . - pslave1860), data = south.counties, weights = sample.size.res)

sph.resent.iv <- ivreg(update(base.iv.form, resent ~ log(1+slavesperwhite) + . - pslave1860| .), data = south.counties, weights = sample.size.res, subset = cottonsuit > 0)

sph.res.first <- lm(update(base.first.form, log(1+slavesperwhite) ~ .), data = south.counties, weights = sample.size, na.action = na.exclude)

stargazer(sph.dem.full, sph.iv, sph.aff.full, sph.aff.iv, sph.resent.full,sph.resent.iv,
          keep = "slavesperwhite", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Log(1 + Slaves per White, 1860)"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"),
          title = "Effect of slavery on white partisan identification, views on affirmative action, and racial resentment with an alternative definition of slavery: slaves per slaveholder.", label = "t:slavesperholder")

## Individual results (whites)

varlabs <- c("Prop. Slave, 1860", "Log(County Area)", "Ruggedness", "Land Inequality, 1860", "Prop. Small Farm, 1860", "Log(Total Pop., 1860)", "Log(Farm Value per  acre, 1860)", "Prop. Free Black, 1860", "Log(Improved Acres, 1860)", "Rail Access, 1860", "Water Access, 1860", "Educ: HS Grad", "Educ: Some College", "Educ: 2-year degree", "Educ: 4-year degree", "Educ: Postgrad", "Family Inc: \\$20,000-50,000", "Family Inc: \\$50,000-100,000", "Family Inc: \\$100,000-150,000", "Family Inc: \\$150,000+", "Religion Import.", "Female", "Age", "Prop. Black in Zip, 2000", "Log(Median Zip Code Inc, 2010)", "White Unemp. Rate, 2010-2014", "Log(White-Black Median Inc Ratio)")

ind.dem.fe <- glm(dem ~ pslave1860 + state.abb*as.factor(year), data = s.whites, family=binomial(), weights = weights)

ind.dem.1860 <- glm(update(base1860.form, dem ~ . + state.abb*as.factor(year)), data = s.whites, family=binomial(), weights = weights)
ind.dem.1860.rse <- robust.se(ind.dem.1860, clvar = "fips")

ind.dem.full <- glm(update(ind.form, dem ~ .), data = s.whites, family=binomial(), weights = weights)
ind.dem.full.rse <-robust.se(ind.dem.full, clvar = "fips")

ind.dem.context <- glm(update(context.form, dem ~ .), data = s.whites, family = binomial(), weights = weights)
ind.dem.context.rse <- robust.se(ind.dem.context, clvar = "fips")

ind.dem.int <- glm(update(ind.int.form, dem ~ .), data = s.whites, family=binomial(), weights = weights)
ind.dem.int.rse <-robust.se(ind.dem.int, clvar = "fips")

ind.dem.context.int <- glm(update(context.int.form, dem ~ .), data = s.whites, family = binomial(), weights = weights)
ind.dem.context.int.rse <- robust.se(ind.dem.context.int, clvar = "fips")



ind.aff.fe <- glm(affirm ~ pslave1860 + state.abb*as.factor(year), data = s.whites, family=binomial(), weights = weights)

ind.aff.1860 <- glm(update(base1860.form, affirm ~ . + state.abb*as.factor(year)), data = s.whites, family=binomial(), weights = weights)
ind.aff.1860.rse <- robust.se(ind.aff.1860, clvar = "fips")

ind.aff.full <- glm(update(ind.form, affirm ~ .), data = s.whites, family=binomial(), weights = weights)
ind.aff.full.rse <- robust.se(ind.aff.full, clvar = "fips")

ind.aff.context <- glm(update(context.form, affirm ~ .), data = s.whites, family = binomial(), weights = weights)
ind.aff.context.rse <- robust.se(ind.aff.context, clvar = "fips")

ind.aff.int <- glm(update(ind.int.form, affirm ~ .), data = s.whites, family=binomial(), weights = weights)
ind.aff.int.rse <-robust.se(ind.aff.int, clvar = "fips")

ind.aff.context.int <- glm(update(context.int.form, affirm ~ .), data = s.whites, family = binomial(), weights = weights)
ind.aff.context.int.rse <- robust.se(ind.aff.context.int, clvar = "fips")


ind.resent.fe <- lm(resent ~ pslave1860 + state.abb*as.factor(year), data = s.whites, weights = weights)

ind.resent.1860 <- lm(update(base1860.form, resent ~ . + state.abb*as.factor(year)), data = s.whites, weights = weights)
ind.resent.1860.rse <- robust.se(ind.resent.1860, clvar = "fips")

ind.resent.full <- lm(update(ind.form, resent ~ .), data = s.whites, weights = weights)
ind.resent.full.rse <- robust.se(ind.resent.full, clvar = "fips")

ind.resent.context <- lm(update(context.form, resent ~ .), data = s.whites, weights = weights)
ind.resent.context.rse <- robust.se(ind.resent.context, clvar = "fips")

ind.resent.int <- lm(update(ind.int.form, resent ~ .), data = s.whites, weights = weights)
ind.resent.int.rse <- robust.se(ind.resent.int, clvar = "fips")

ind.resent.context.int <- lm(update(context.int.form, resent ~ .), data = s.whites, weights = weights)
ind.resent.context.int.rse <- robust.se(ind.resent.context.int, clvar = "fips")


ind.full.table <- stargazer(ind.dem.1860, ind.dem.full, ind.dem.context, ind.aff.1860, ind.aff.full, ind.aff.context, ind.resent.1860, ind.resent.full,ind.resent.context,
          omit = c("state","year", "latitude", "longitude"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser", "bic", "rsq", "aic"),
          se = list(ind.dem.1860.rse[,2], ind.dem.full.rse[,2], ind.dem.context.rse[,2], ind.aff.1860.rse[,2], ind.aff.full.rse[,2], ind.aff.context.rse[,2], ind.resent.1860.rse[,2], ind.resent.full.rse[,2], ind.resent.context.rse[,2]), column.sep.width = "0pt",
          covariate.labels = varlabs, float = FALSE, header = FALSE, add.lines = list(rep("", 9), ch.row("State-Year Fixed Effects", rep(TRUE,9)), ch.row("Latitude/Longitude", rep(TRUE, 9)), rep("", 9)), multicolumn = TRUE, dep.var.labels = rep(c("Prop Democrat", "Affirm. Action", "Racial Resentment"), each = 3))


varlabs.int <- c("Prop. Slave $\\times$ Educ: HS Grad", "Prop. Slave $\\times$ Educ: Some College", "Prop. Slave $\\times$ Educ: 2-year degree", "Prop. Slave $\\times$ Educ: 4-year degree", "Prop. Slave $\\times$ Educ: Postgrad", "Prop. Slave $\\times$ Family Inc: \\$20,000-50,000", "Prop. Slave $\\times$ Family Inc: \\$50,000-100,000", "Prop. Slave $\\times$ Family Inc: \\$100,000-150,000", "Prop. Slave $\\times$ Family Inc: \\$150,000+", "Prop. Slave $\\times$ Religion Import.", "Prop. Slave $\\times$ Female", "Prop. Slave $\\times$ Age", "Prop. Slave $\\times$ Prop. Black in Zip, 2000", "Prop. Slave $\\times$ Log(Median Zip Code Inc, 2010)", "Prop. Slave $\\times$ White Unemp. Rate, 2010-2014", "Prop. Slave $\\times$ Log(White-Black Median Inc Ratio)")

int.full.table <- stargazer(ind.dem.int, ind.dem.context.int, ind.aff.int, ind.aff.context.int, ind.resent.int, ind.resent.context.int,
          keep = c("pslave1860:"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser", "bic", "rsq", "aic"),
          se = list(ind.dem.int.rse[,2], ind.dem.context.int.rse[,2], ind.aff.int.rse[,2], ind.aff.context.int.rse[,2], ind.resent.int.rse[,2], ind.resent.context.int.rse[,2]), column.sep.width = "0pt",
          covariate.labels = varlabs.int, float = FALSE, header = FALSE, add.lines = list(rep("", 6), ch.row("State-Year Fixed Effects", rep(TRUE,6)), ch.row("Lower-Order Terms", rep(TRUE,6)), ch.row("Individual-Level Covariates", rep(TRUE, 6)), ch.row("Contextual Covariates", rep(c(FALSE,TRUE), 3)), rep("", 6)), multicolumn = TRUE, dep.var.labels = rep(c("Prop Democrat", "Affirm. Action", "Racial Resentment"), each = 2))


## Livestock instead of land for civil war destruction

south.counties$civil.des.lstock <- with(south.counties, (livstock - livstock1870)/livstock)
is.na(south.counties$civil.des.lstock) <- which(south.counties$livstock == 0)
cnty.dem.civil.lstock <- lm(update(base1860.form, dem ~ . + civil.des.lstock), data = south.counties, weights = sample.size)

cnty.aff.civil.lstock <- lm(update(base1860.form, affirm ~ . + civil.des.lstock), data = south.counties, weights = sample.size)

cnty.resent.civil.lstock <- lm(update(base1860.form, resent ~ . + civil.des.lstock), data = south.counties, weights = sample.size.res)

livestock.tab <- stargazer(cnty.dem.civil.lstock, cnty.aff.civil.lstock, cnty.resent.civil.lstock,
          keep = c("pslave1860","civil.des.lstock"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
                           covariate.labels = c("Prop. Slave, 1860", "Livestock Value Loss, 1860-1870"), dep.var.labels = c("Prop. Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 3), ch.row("State Fixed Effects", rep(TRUE, 3)), ch.row("1860 Covariates", rep(TRUE, 3)), rep("", 3)), multicolumn = FALSE)



## Inequality outcomes
cnty.ineq40.full <- lm(update(base1860.form, I(whtlwage1940-blklwage1940) ~ .), data = south.counties)

cnty.ineq40.iv <- ivreg(update(base.iv.form, I(whtlwage1940-blklwage1940) ~ .), data = south.counties, subset = cottonsuit > 0)

cnty.ineq40.rform <- lm(update(rform.form, I(blklwage1940) ~ .), data = wh.counties, !(state.abb %in% st.list) & !(state.abb %in% c("MD", "DE", "MO")) & cottonsuit > 0)

cnty.ineq.full <- lm(update(base1860.form, log(wbincratio2014) ~ .), data = south.counties)

cnty.ineq.iv <- ivreg(update(base.iv.form, log(wbincratio2014) ~ .), data = countydata, subset = state.abb %in% st.list & cottonsuit > 0)

cnty.inc.full <- lm(update(base1860.form, log(w.med.income2014) ~ .), data = south.counties)

cnty.inc.iv <- ivreg(update(base.iv.form, log(w.med.income2014) ~ .), data = south.counties, subset = cottonsuit > 0)

cnty.inc.rform <- lm(update(rform.form, log(w.med.income2014) ~ .), data = wh.counties, !(state.abb %in% st.list) & !(state.abb %in% c("MD", "DE", "MO")) & cottonsuit > 0)

ineq.tab <- stargazer(cnty.ineq40.full, cnty.ineq40.iv, cnty.ineq.full, cnty.ineq.iv, cnty.inc.full, cnty.inc.iv,
          keep = "pslave1860", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860"), dep.var.labels = c("log White Wage - log Black Wages, 1940", "log White Income - log Black Income, 1990", "log Median Income, 2000"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE, 6)), ch.row("Geographic Controls", rep(TRUE, 6)), ch.row("1860 Covariates", rep(c(TRUE, FALSE), 3)), rep("", 7)), multicolumn = FALSE)

ineq.dem <- lm(dem ~ log(wbincratio2014) + state.abb, data = south.counties, weights = sample.size)

ineq.dem.full <- lm(update(base1860.form, dem ~ log(wbincratio2014) + .), data = south.counties, weights = sample.size)

ineq.aff <- lm(affirm ~ log(wbincratio2014) + state.abb, data = south.counties, weights = sample.size)

ineq.aff.full <- lm(update(base1860.form, affirm ~ log(wbincratio2014) + .), data = south.counties, weights = sample.size)

ineq.resent <- lm(resent ~ log(wbincratio2014) + state.abb, data = south.counties, weights = sample.size.res)

ineq.resent.full <- lm(update(base1860.form, resent ~ log(wbincratio2014) + .), data = south.counties, weights = sample.size.res)

ineq2.tab <- stargazer(ineq.dem, ineq.dem.full, ineq.aff, ineq.aff.full, ineq.resent, ineq.resent.full,
          keep = c("wbincratio2014", "pslave1860"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
                       covariate.labels = c("log White-Black Income Ratio, 2014","Prop. Slave, 1860"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 7), ch.row("State Fixed Effects", rep(TRUE, 6)), ch.row("1860 Covariates", rep(TRUE, 6)), rep("", 7)), multicolumn = FALSE)

## Interaction of slavery with income

ind.dem.inc <- glm(update(base1860.form, dem ~ . + pslave1860*log(inc.mid)), data = s.whites, family=binomial())
ind.dem.inc.rse <-robust.se(ind.dem.inc, clvar = "fips")

ind.aff.inc <- glm(update(base1860.form, affirm ~ . + pslave1860*log(inc.mid) ), data = s.whites, family=binomial())
ind.aff.inc.rse <- robust.se(ind.aff.inc, clvar = "fips")

ind.resent.inc<- lm(update(base1860.form, resent ~ . + pslave1860*log(inc.mid)), data = s.whites)
ind.resent.inc.rse <- robust.se(ind.resent.inc, clvar = "fips")

inc.int.tab <-  stargazer(ind.dem.inc, ind.aff.inc, ind.resent.inc,
          keep = c("pslave1860", "inc.mid"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser", "bic"),
          se = list(ind.dem.inc.rse[,2], ind.aff.inc.rse[,2], ind.resent.inc.rse[,2]),
          covariate.labels = c("Prop. Slave, 1860", "Income", "Prop. Slave $\\times$ Income"), dep.var.labels = c("Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 3), ch.row("State Fixed Effects", rep(TRUE, 3)), ch.row("1860 Covariates", rep(TRUE, 3)), ch.row("Clustered SEs", rep(TRUE, 3)), rep("", 3)), multicolumn = FALSE)

## How much the black population declined?
south.counties$blk.shrink.4020 <- with(south.counties, blkprop20- blkprop40)
cnty.dem.blkshrink <- lm(update(base1860.form, dem ~ pslave1860*blk.shrink.4020 + .), data = south.counties, weights = sample.size)

cnty.aff.blkshrink <- lm(update(base1860.form, affirm ~ pslave1860*blk.shrink.4020 + .), data = south.counties, weights = sample.size)

cnty.resent.blkshrink <- lm(update(base1860.form, resent ~ pslave1860*blk.shrink.4020 + .), data = south.counties, weights = sample.size.res)

south.counties$blk.shrink.7020 <- with(south.counties, blkprop20- blkprop70)
cnty.dem.blkshrink.70 <- lm(update(base1860.form, dem ~ pslave1860*blk.shrink.7020 + .), data = south.counties, weights = sample.size)

cnty.aff.blkshrink.70 <- lm(update(base1860.form, affirm ~ pslave1860*blk.shrink.7020  + .), data = south.counties, weights = sample.size)

cnty.resent.blkshrink.70 <- lm(update(base1860.form, resent ~ pslave1860*blk.shrink.7020 + .), data = south.counties, weights = sample.size.res)

blkshrink.tab <- stargazer(cnty.dem.blkshrink, cnty.dem.blkshrink.70, cnty.aff.blkshrink, cnty.aff.blkshrink.70, cnty.resent.blkshrink, cnty.resent.blkshrink.70,
          keep = c("pslave1860", "blk.shrink.4020", "blk.shrink.7020"), style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860", "Prop Black Decline, 1940-1920", "Prop Black Decline, 1970-1920", "Prop Slave $\\times$ Black Decline, 1940-1920", "Prop Slave $\\times$ Black Decline, 1970-1920"),
                           dep.var.labels = c( "Prop Democrat", "Affirm. Action", "Racial Resentment"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 3), ch.row("State Fixed Effects", rep(TRUE, 6)), ch.row("1860 Covariates", rep(TRUE, 6)), rep("", 3)), multicolumn = FALSE)

## Inflows and outflows
outflow.fe <- lm(I(outflow/totpop00) ~ pslave1860 + state.abb, data = countydata, subset = state.abb %in% st.list)

outflow.1860 <- lm(update(base1860.form, I(outflow/totpop00) ~ .), data = countydata, subset = state.abb %in% st.list)

inflow.fe <- lm(I(inflow/totpop00) ~ pslave1860 + state.abb, data = countydata, subset = state.abb %in% st.list)

inflow.1860 <- lm(update(base1860.form, I(inflow/totpop00) ~ .), data = countydata, subset = state.abb %in% st.list)

outmig.tab <- stargazer(inflow.1860, outflow.1860, #cnty.dem.flow, cnty.aff.flow, cnty.resent.flow,
          keep = "pslave1860", style = "apsr", omit.stat = c("ll", "adj.rsq", "F", "ser"),
          covariate.labels = c("Prop. Slave, 1860"), dep.var.labels = c("In-migration", "Out-migration"), column.sep.width = "5pt", float = FALSE, header = FALSE, add.lines = list(rep("", 3), ch.row("State Fixed Effects", rep(TRUE, 2)), ch.row("1860 Covariates", rep(TRUE, 2)), rep("", 3)), multicolumn = FALSE)
```

